Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-05-22 writing/embedded_meta_learning_main.tex
Notation, notation, notation

\[\hat{y} = \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
where $f_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[f_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)\]

@@

\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(f_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]

@@

\[\hat{z}_{new} = f_{z_{\text{function}}}(z_{go}) \qquad \text{where } f_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]

>>>>

\[\hat{y} = \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\]
where $F_{D_1}$ is the transformation the meta-learner guesses for the training dataset $D_1$:
\[F_{D_1} \text{ is parameterized by } \mathcal{H}\left(\mathcal{M}\left( \left\{\left(\mathcal{I}\left(x_0\right), \mathcal{T}\left(y_0\right) \right), \left(\mathcal{I}\left(x_1\right), \mathcal{T}\left(y_1\right) \right), ... \right\}\right)\right)\]

@@

\[\mathbb{E}_{(x, y)\in {D}_2} \left[ \mathfrak{L}\left(y, \mathcal{O}\left(F_{D_1}\left(\mathcal{I} \left(x\right)\right) \right)\right)\right]\]

@@

\[\hat{z}_{new} = F_{z_{\text{function}}}(z_{go}) \qquad \text{where } F_{z_{\text{meta}}} \text{ is parameterized by } \mathcal{H}\left(z_{\text{meta}}\right)\]
